\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.5in, top=0.35in, bottom=0.35in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{xcolor}

% Remove page numbers
\pagestyle{empty}

% Section formatting
\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}

% Tighter lists
\setlist[itemize]{nosep, leftmargin=13pt, topsep=1pt, parsep=0pt, itemsep=1pt}

% Commands
\newcommand{\role}[4]{%
  \vspace{2pt}
  \noindent\textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
  \vspace{1pt}
}

\newcommand{\project}[3]{%
  \vspace{2pt}
  \noindent\textbf{#1} \hfill \textit{#2} \\
  {\small #3}
  \vspace{1pt}
}

\begin{document}

% Header
\begin{center}
  {\Large\bfseries VIBHOR KASHMIRA} \\[2pt]
  Detroit, MI \enspace$\cdot$\enspace (313) 746-0667 \enspace$\cdot$\enspace vibhorkashmira@gmail.com \enspace$\cdot$\enspace \href{https://bellerophon95.github.io/mypage}{bellerophon95.github.io/mypage}
\end{center}

\vspace{-6pt}
\noindent Fullstack engineer specializing in event-driven backend systems, data-intensive applications, and frontend performance optimization.

% Experience
\section{Experience}

\role{Software Engineer (AI)}{Aug 2025 -- Present}{Vizly Inc.}{Southfield, MI}
\begin{itemize}
  \item Architected a distributed agent execution system with a full ReAct reasoning loop, human-in-the-loop approval gates, autonomous actions, and recursive fallback --- coordinated via database-backed message passing, cron scheduling, idempotent retries, and durable state across human interrupts.
  \item Built an MCP server (FastAPI) exposing tools for agents to load code samples, read/write state, and query metadata; designed a Supabase-backed context layer that decouples heavy datasets from LLM prompts, cutting token usage 60\%.
  \item Architected an RPyC bridge on AWS EKS for streaming S3 datasets to JupyterHub. Deployed with Docker/ECR, Prometheus, Grafana, and OpenTelemetry. Cut infrastructure costs 10\% via FinOps.
  \item Shipped the Next.js / Vercel AI SDK surfaces on top of these systems --- streaming chat UI, approval flows, and live run-status views backed by Supabase realtime --- to deliver agent features end-to-end.
\end{itemize}

\role{Software Engineer}{Jun 2017 -- Jun 2023}{Sprinklr Inc.}{Gurugram, India}
\begin{itemize}
  \item Led strategic migration of legacy Engagement feed APIs to GraphQL, resulting in 15\% reduction in response time and 25\% decrease in network payload.
  \item Reduced infrastructure costs by 10\% and maintained SLA requirements by spearheading cloud-based approaches to handle skewed workloads using AWS Lambda and EC2 for the Display module.
  \item Designed and built robust GraphQL resolvers for Engagement and Display modules, enabling seamless data aggregation from multiple sources while maintaining strict performance SLAs.
  \item Achieved 10\% increase in request responsiveness for key Engagement paths by leveraging gRPC for inter-service communication, caching strategy optimizations and leveraging reactive principles using Spring Webflux. Set up continuous profiling practices to prevent service degradation.
  \item Engineered event-driven architecture using Kafka pub-sub message queues, processing over 10,000 messages per second with end-to-end observability and event tracing.
  \item Optimized MongoDB by progressive sharding (driven by event tracing data), queries and indexing strategies, for third pane, macro and publisher happy paths, reducing query latency by 15\% and improving overall application responsiveness for the main Engagement feed call and 14 key Governance asset classes.
  \item Leveraged comprehensive monitoring solutions with ELK Stack (Elasticsearch, Logstash, Kibana), reducing MTTR for engagement-tagged tickets by using optimal triaging strategies.
  \item Achieved near-zero-downtime deployments and triple 9 across Kubernetes production environments.
  \item Established automated testing frameworks using TestNG, Gatling, and REST Assured with Jenkins CI/CD, increasing test coverage to 80\% and reducing regression issues by 20\%.
  \item Mentored junior developers through code reviews and pair programming sessions.
\end{itemize}

% Projects
\section{Projects}

\project{Rentaroost}{Jul -- Aug 2024}{\href{https://bellerophon95.github.io/mypage/rentaroost/}{bellerophon95.github.io/mypage/rentaroost/}}
\begin{itemize}
  \item Designed CQRS-style architecture with GraphQL (Netflix DGS) for user-facing queries, gRPC for internal reads, and Kafka for async mutations; deployed on Kubernetes.
  \item Built a real-time dynamic pricing pipeline on Kafka + Flink (with watermarking for out-of-order events) that adjusts prices from view/booking streams via Redis TTLs; orchestrated payment (Stripe) and booking flows with the Kafka Saga pattern on Spring WebFlux.
\end{itemize}

% Skills
\section{Technical Skills}

\noindent\textbf{Backend:} Python (FastAPI), Java (Spring Boot), gRPC, GraphQL (Netflix DGS), Spring WebFlux, REST \\
\textbf{Data \& Streaming:} Apache Kafka, Apache Flink, MongoDB, Redis, Supabase (PostgreSQL), Qdrant \\
\textbf{Infrastructure:} AWS (EKS, S3, Lambda, EC2), Kubernetes, Docker, Terraform, CI/CD (Jenkins, GitHub Actions) \\
\textbf{Frontend:} Next.js, React, Vercel AI SDK, GraphQL clients \\
\textbf{Observability:} Prometheus, Grafana, OpenTelemetry, ELK Stack, Langfuse \\
\textbf{AI Tooling:} LangGraph, RAG (hybrid retrieval, cross-encoder reranking), RAGAS, MCP

% Education
\section{Education}

\noindent\textbf{Wayne State University} -- M.S. in Computer Science (Dean's List) \hfill Aug 2023 -- Dec 2024 \\
\textbf{The LNMIIT} -- B.Tech in Computer Science \hfill Aug 2013 -- May 2017

\end{document}