\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.5in, top=0.4in, bottom=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{xcolor}

% Remove page numbers
\pagestyle{empty}

% Section formatting
\titleformat{\section}{\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

% Tighter lists
\setlist[itemize]{nosep, leftmargin=14pt, topsep=1pt, parsep=0pt, itemsep=1.5pt}

% Commands
\newcommand{\role}[4]{%
  \vspace{3pt}
  \noindent\textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
  \vspace{1pt}
}

\newcommand{\project}[3]{%
  \vspace{3pt}
  \noindent\textbf{#1} \hfill \textit{#2} \\
  {\small #3}
  \vspace{1pt}
}

\begin{document}

% Header
\begin{center}
  {\Large\bfseries VIBHOR KASHMIRA} \\[3pt]
  Detroit, MI \enspace$\cdot$\enspace (313) 746-0667 \enspace$\cdot$\enspace vibhorkashmira@gmail.com \enspace$\cdot$\enspace \href{https://bellerophon95.github.io/mypage}{bellerophon95.github.io/mypage}
\end{center}

\vspace{-4pt}
\noindent Software engineer with 7+ years building AI-powered products, event-driven systems, and data pipelines. Currently building agentic execution systems, evaluation infrastructure, and context management tooling for LLM workflows at an acquired YC-backed AI company.

% Experience
\section{Experience}

\role{Software Engineer (AI)}{Aug 2025 -- Present}{Vizly Inc. (YC-backed, acquired by Aggregate Intelligence)}{Southfield, MI}
\begin{itemize}
  \item Architected distributed agent execution system with a full ReAct reasoning loop, human-in-the-loop approval gates, autonomous actions layer, and recursive fallback. Coordinated via database-backed message passing, cron-driven scheduling, idempotent retries, and durable state persistence across human interrupts.
  \item Built MCP server (FastAPI) exposing tools for AI agents to load code samples, read/write to the database, and query metadata --- enabling autonomous task execution across Vizly's data analysis platform.
  \item Designed context management layer (Supabase) decoupling heavy datasets from LLM prompts, reducing token usage by 60\%. Architected RPyC bridge on AWS EKS for streaming S3 datasets to JupyterHub; cut infrastructure costs by 10\% via FinOps.
\end{itemize}

\role{Software Engineer}{Jun 2017 -- Jun 2023}{Sprinklr Inc.}{Gurugram, India}
\begin{itemize}
  \item Led migration of legacy Engagement feed APIs to GraphQL, reducing response time by 15\% and network payload by 25\%. Leveraged gRPC and reactive processing (Spring WebFlux) for key performance paths.
  \item Engineered event-driven architecture using Kafka, processing 10,000+ messages/sec with end-to-end observability. Optimized MongoDB via progressive sharding driven by event tracing data, reducing query latency by 15\%.
  \item Achieved 99.9\% availability across Kubernetes environments with near-zero-downtime deployments. Reduced infrastructure costs by 10\% via AWS Lambda/EC2 for skewed workloads. Automated testing (Gatling, REST Assured) via Jenkins CI/CD.
  \item Mentored junior developers through code reviews and pair programming, reducing regression issues by 20\%.
\end{itemize}

% Projects
\section{Projects}

\project{Nexus -- Multi-Agent RAG System}{May 2024 -- Present}{\href{https://project-nexus.duckdns.org}{project-nexus.duckdns.org} $\cdot$ \href{https://github.com/bellerophon95/nexus}{github.com/bellerophon95/nexus}}
\begin{itemize}
  \item Designed continuous evaluation system with 124-sample golden dataset, RAGAS threshold monitoring with automated violation alerting (context precision, answer relevancy), and a production-to-golden promotion workflow for iterative grounding improvement.
  \item Built per-response trace decomposition surfacing latency, token cost, grounding score, relevance score, guardrail status, and per-source citation match percentages in a real-time observability dashboard.
  \item Engineered multi-agent RAG pipeline (LangGraph) with hybrid retrieval (Qdrant dense + sparse), BGE-Reranker-v2 cross-encoder, and a Self-RAG validator triggering re-retrieval on insufficient grounding. Exposed runtime tuning of retrieval sensitivity, reranking depth, and max agentic loops.
  \item Deployed full-stack on Railway/Vercel with FastAPI, Next.js 15, Supabase, Upstash Redis semantic caching, and GitHub Actions CI/CD. Solo-built across 80 commits.
\end{itemize}

\project{Rentaroost}{May -- Jun 2024}{\href{https://bellerophon95.github.io/mypage/rentaroost/}{bellerophon95.github.io/mypage/rentaroost/}}
\begin{itemize}
  \item Built real-time dynamic pricing pipeline using Apache Kafka and Apache Flink with watermark handling for out-of-order events. Implemented Kafka Saga pattern for distributed transactions across payment (Stripe) and booking services. Designed CQRS architecture with GraphQL (Netflix DGS), gRPC, and Kafka. Deployed on Kubernetes.
\end{itemize}

% Skills
\section{Technical Skills}

\noindent\textbf{Backend:} Python (FastAPI), Java (Spring Boot), gRPC, GraphQL (Netflix DGS), Spring WebFlux, REST \\
\textbf{Data \& Streaming:} Apache Kafka, Apache Flink, MongoDB, Redis, Supabase (PostgreSQL), Qdrant \\
\textbf{Infrastructure:} AWS (EKS, S3, Lambda, EC2), Kubernetes, Docker, Terraform, CI/CD (Jenkins, GitHub Actions) \\
\textbf{Observability:} Prometheus, Grafana, OpenTelemetry, ELK Stack, Langfuse \\
\textbf{AI Tooling:} LangGraph, RAG (hybrid retrieval, cross-encoder reranking), RAGAS, MCP, Vercel AI SDK

% Education
\section{Education}

\noindent\textbf{Wayne State University} -- M.S. in Computer Science (Dean's List) \hfill Aug 2023 -- Dec 2024 \\
\textbf{The LNMIIT} -- B.Tech in Computer Science \hfill Aug 2013 -- May 2017

\end{document}
